### 2025-07-11 factor-analysis.qmd
20250711 - players with lowest/highest levels on components/factors

head(efa3factorModified_factorScores)
```

@@

```{r}
efa3factorModified_factorScores[which.max(efa3factorModified_factorScores[,"F1"]),]
```

```{r}
dataForFA[which.max(efa3factorModified_factorScores[,"F1"]), c("player_display_name", "season", factor1vars)]
```

```{r}
efa3factorModified_factorScores[which.max(efa3factorModified_factorScores[,"F2"]),]
```

```{r}
dataForFA[which.max(efa3factorModified_factorScores[,"F2"]), c("player_display_name", "season", factor2vars)]
```

```{r}
efa3factorModified_factorScores[which.max(efa3factorModified_factorScores[,"F3"]),]
```

```{r}
dataForFA[which.max(efa3factorModified_factorScores[,"F3"]), c("player_display_name", "season", factor3vars)]
```

@@

head(cfa3factorModified_factorScores)
```

@@

```{r}
cfa3factorModified_factorScores[which.max(cfa3factorModified_factorScores[,"F1"]),]
```

```{r}
dataForFA[which.max(cfa3factorModified_factorScores[,"F1"]), c("player_display_name", "season", factor1vars)]
```

```{r}
cfa3factorModified_factorScores[which.max(cfa3factorModified_factorScores[,"F2"]),]
```

```{r}
dataForFA[which.max(cfa3factorModified_factorScores[,"F2"]), c("player_display_name", "season", factor2vars)]
```

```{r}
cfa3factorModified_factorScores[which.max(cfa3factorModified_factorScores[,"F3"]),]
```

```{r}
dataForFA[which.max(cfa3factorModified_factorScores[,"F3"]), c("player_display_name", "season", factor3vars)]
```

>>>>

head(efa3factorModified_factorScores)

dataForFA_efa <- cbind(dataForFA, efa3factorModified_factorScores)
```

@@

```{r}
dataForFA_efa %>% 
  arrange(-F1) %>% 
  select(player_display_name, season, F1, all_of(factor1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_efa %>% 
  arrange(F1) %>% 
  select(player_display_name, season, F1, all_of(factor1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_efa %>% 
  arrange(-F2) %>% 
  select(player_display_name, season, F2, all_of(factor2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_efa %>% 
  arrange(F2) %>% 
  select(player_display_name, season, F2, all_of(factor2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_efa %>% 
  arrange(-F3) %>% 
  select(player_display_name, season, F3, all_of(factor3vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_efa %>% 
  arrange(F3) %>% 
  select(player_display_name, season, F3, all_of(factor3vars)) %>% 
  na.omit() %>% 
  head()
```

@@

head(cfa3factorModified_factorScores)

dataForFA_cfa <- cbind(dataForFA, cfa3factorModified_factorScores)
```

@@

```{r}
dataForFA_cfa %>% 
  arrange(-F1) %>% 
  select(player_display_name, season, F1, all_of(factor1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_cfa %>% 
  arrange(F1) %>% 
  select(player_display_name, season, F1, all_of(factor1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_cfa %>% 
  arrange(-F2) %>% 
  select(player_display_name, season, F2, all_of(factor2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_cfa %>% 
  arrange(F2) %>% 
  select(player_display_name, season, F2, all_of(factor2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_cfa %>% 
  arrange(-F3) %>% 
  select(player_display_name, season, F3, all_of(factor3vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataForFA_cfa %>% 
  arrange(F3) %>% 
  select(player_display_name, season, F3, all_of(factor3vars)) %>% 
  na.omit() %>% 
  head()
```

### 2025-07-11 pca.qmd
20250711 - players with lowest/highest levels on components/factors

```{r}
dataMergedWithPCA %>% 
  arrange(-TC1) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component1vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC1) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component1vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC2) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component2vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC2) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component2vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC3) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component3vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC3) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component3vars))
```

>>>>

```{r}
dataMergedWithPCA %>% 
  arrange(-TC1) %>% 
  select(player_display_name, season, week, TC1, all_of(component1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC1) %>% 
  select(player_display_name, season, week, TC1, all_of(component1vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC2) %>% 
  select(player_display_name, season, week, TC2, all_of(component2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC2) %>% 
  select(player_display_name, season, week, TC2, all_of(component2vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC3) %>% 
  select(player_display_name, season, week, TC3, all_of(component3vars)) %>% 
  na.omit() %>% 
  head()
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC3) %>% 
  head %>% 
  select(player_display_name, season, week, TC3, all_of(component3vars)) %>% 
  na.omit() %>% 
  head()
```
